Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
SoA

    \section{State of the art}
    \label{SoA}
    In this Section we present PCG works relevant to the Level generation for the
    Angry Birds video game. Renz et al. \cite{Renz, Renz2015TheAB} organized an AI
    competition with the aim of developing intelligent agents that could play new
    Angry Birds levels better than the best human players. The competition was then
    collocated in other AI conferences. In order to train and test these agents,
    more novel and some times difficult levels must be generated. A related
    competition was then proposed by Stephenson et al. \cite{Stephenson} this time
    with the goal of developing a level generator for the game. Several generators
    have been proposed in the following years of competition. M. Katina et al.
    \cite{Kaidan2015} propose a model in which the generation of content is
    controlled by the skill of a player while actively playing the game, the moment
    the player finishes a certain level the algorithm obtains the score and
    generates the next level to be played. Y. Jiang et al. \cite{Jiang2017} proposed
    the use of predefined letter style patterns and combined to create a small pool
    of words and letters used to be combined in order to create levels with text on
    them, the participants would play the game and after that they would be asked if
    they liked the layout of the levels. A search based approach has been also used
    in several works. Laura Calle \cite{lauracalle} proposed a method in which the 
    pieces in the game are arranged in groups using the gravity of the game to 
    create structures that are later evolved into more complex levels, this method 
    was used as a base to work with since it used a modified version of the angry 
    birds game that was able to obtain the data of a level after a simulation.
    %%%
    % TO DO: Laura´s work here 
    %%%

>>>>

\section{State of the art}
\label{SoA}
In this Section, we present PCG works relevant to the level generation for
the Angry Birds video game. Renz et al. \cite{Renz, Renz2015TheAB} organized
an AI competition to develop intelligent agents that could play new  Angry
Birds levels better than the best human players. The competition was then
collocated in other AI conferences. To better train and test agents, more
novel and some times, challenging levels must be generated. Stephenson et
al. proposed a related competition this time with the goal of developing a
level generator for the game. Researchers have proposed several generators
in the following years of competition. M. Katina et al.  \cite{Kaidan2015}
propose a model in which the algorithm controls the generation of content by
using the skill of a player, while she is actively playing the game. The
moment the player finishes a certain level, the algorithm obtains the score
and generates the next level to play. Y. Jiang et al. \cite{Jiang2017}
proposed the use of predefined letter patterns and combined them to create a
small pool of words and letters used to create levels with text on them.
Users would play the game, and after that,   asked them if they liked the
layout of the Levels.  Several researchers follow a search-based approach.
Calle et al. \cite{lauracalle} propose a free-search method to generate
levels.  For this, lists of blocks are placed in the game by the algorithm,
and those maintaining their positions against gravity are selected to build
structures. The resulting structures continue evolving into more complex
levels. That work is the basis of our current proposal, and since we are
using a modified version of the Angry Birds game, that can obtain data of a
level after a simulation.
    %%%
    % TO DO: Laura´s work here 
    %%%
